PM Component Paper Plots

### 2021-05-25 code/data-viz/forest-plots-color.Rmd
plot, table, map

>>>>

```{r - Components urban}
data <- out.pmc.urbanicity %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz,
         Loc.Set == "urban") %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
  )

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','pmc-urban.png'), width = 6.5, height = 6.5)
```

```{r - Factors urban}
data <- out.fac.urbanicity %>% 
  filter(Index %in% So.main,
         Cause %in% cuz,
         Loc.Set == "urban") %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
  )

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','fac-urban.png'), width = 6.5, height = 6.5)
```
